Energy Regulation for Biologically-inspired Robotics

### 2021-09-19 latex/nserc/contributions.tex
Editing the contributions again, still not done and too long.

Over the course of my career, I have enjoyed several extracurricular roles which
developed my communication, interpersonal, and leadership skills.
What follows is a brief description of some of these roles.
\begin{itemize}
\item \textbf{Lionel Massey Fund Co-chair, Massey College, September 2021 -- Present}.
    I am one of six co-chairs for the Lionel Massey Fund, which is the events
    committee for Massey College (an interdisciplinary college at the University
    of Toronto).
    I have already organized 13 events for members of the college, and will
    continue to organize biweekly events throughout the year.
    This role has taught me the logistics and leadership skills required to
    manage large events for 150 people.
    I have also learned to make events accessible to everyone by asking
    questions so I can understand the needs of all attendees.

>>>>

Over the course of my academic career, I have enjoyed several extracurricular
roles which developed my communication, interpersonal, and leadership skills.
What follows is a brief description of some of these roles.
\begin{itemize}
\item \textbf{Lionel Massey Fund Co-chair, Massey College, September 2021 -- Present}.
    I am one of six co-chairs for the Lionel Massey Fund, which is the events
    committee for Massey College (an interdisciplinary college at the University
    of Toronto).
    I have already organized 13 events for members of the college, and will
    continue to organize biweekly events throughout the year.
    This role has taught me the logistics and leadership skills required to
    manage large events for up to 60 people.
    I have also learned to make events accessible to everyone, and to ask
    questions so I can meet the needs of all attendees.
